\documentclass[10pt]{article}

\usepackage[margin=3cm]{geometry}

\usepackage{array, xcolor}
\definecolor{lightgray}{gray}{0.8}
\newcolumntype{L}{>{\raggedleft}p{0.14\textwidth}}
\newcolumntype{R}{p{0.8\textwidth}}
\newcommand\VRule{\color{lightgray}\vrule width 0.5pt}

\usepackage{lipsum}

\usepackage{bibentry}

%%% Работа с русским языком
\usepackage{cmap}					% поиск в PDF
\usepackage{mathtext} 				% русские буквы в формулах
\usepackage[T2A]{fontenc}			% кодировка
\usepackage[utf8]{inputenc}			% кодировка исходного текста
\usepackage[english]{babel}	% локализация и переносы

%%% Работа с картинками
\usepackage{graphicx}  % Для вставки рисунков

% DOCUMENT LAYOUT
%\usepackage{geometry} 
\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}

\usepackage{hyperref}

% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

\title{\textbf{Dmitrii Tereshchenko}\\Academic CV}
\author{}
\date{}

\begin{document}

\maketitle

%\vspace{2em}
\hrule
\section*{Contact Information}
\noindent

	\textit{E-mail}: \\
	\href{mailto:dtereshchenko@hse.ru}{dtereshchenko@hse.ru}  • 
	\href{mailto:dtereshch@gmail.com}{dtereshch@gmail.com}\\
	
	\vspace{0.5em}

	\textit{Social networking} (I'm really not very active there): \\
        \href{https://econtwitter.net/@dtereshch}{Mastodon}  • 
        \href{https://papers.ssrn.com/sol3/cf_dev/AbsByAuth.cfm?per_id=2298921}{SSRN}
	% \href{https://www.hse.ru/staff/dtereshch}{Личная страница}  •
	% \href{https://petrsu.ru/persons/2529/teretshenko}{Академия Google} •
	% \href{https://elibrary.ru/author_items.asp?authorid=640419&pubrole=100&show_refs=1&show_option=0}{eLIBRARY}

\vspace{2em}
\hrule


\section*{Education}
\noindent
\years{2005-2010}Long First Degree in Economics, <<Finance and Credit>> speciality, Petrozavodsk State University. \\

\vspace{2em}
\hrule


\section*{Teaching Experience}
\noindent
\years{2018-\dots}\textit{Senior lecturer}, Department of Economics, St. Petersburg School of Economics and Management, HSE University.

\vspace{1em}
Courses: econometrics, empirical industrial organization, discrete choice and consumer behavior, microeconomics-I, digital skills.

\vspace{1em}
\years{2012-2018}\textit{Lecturer, Senior lecturer}, Faculty of Economics / Institute of Economics and Law, Petrozavodsk State University.

\vspace{1em}
Courses: economics, business communication, corporate social responsibility, economics of land use, real estate economics, economics of land management, economics of machine production, enterprise economics, economics and organization of technical services, economics and production management, basics and organization of business activities, marketing, economic and legal issues of professional activities, economics and management of high technologies, environmental audit and certification. 

\vspace{1em}
\years{2013-2015}\textit{Teacher}, Derzhavin Lyceum, Petrozavodsk.

\vspace{1em}
Courses: economics
\vspace{2em}
\hrule


\section*{Research Experience}
\noindent
\years{2022-\dots}\textit{Junior researcher}, Center for Market Studies and Spatial Economics, HSE University.\\
\years{2019-2019}\textit{Junior researcher}, International Centre for Health Economics, Management, and Policy, HSE University.
\vspace{2em}
\hrule


\section*{Work in Progress}
\noindent
\years{In progress}Do institutions affect innovations in regions? Evidence from Russia.\\
\years{In progress}Empirical estimation of demand of spatially heterogeneous consumers on retail.

\vspace{2em}
\hrule


\section*{Publications}
\noindent
\subsection*{In English}
\noindent
\years{2023}Shcherbakov,  V.  S.  and  Tereshchenko,  D.  S.  (2023).  The  verification  of  regional  capital  mobility in the Russian Federation: A spatial econometric approach. St Petersburg University Journal of Economic Studies, 39 (1), pp. 102–126. \url{https://doi.org/10.21638/spbu05.2023.105}.

\vspace{1em}

\years{2021}Tereshchenko, D. S. and Shcherbakov, V. S. (2021). The impact of scientific activity of universities on economic and innovative development. Ekonomika regiona [Economy of region], 17 (1), 223-234, \url{https://doi.org/10.17059/ekon.reg.2021-1-17}.

\subsection*{In Russian}
\noindent
\years{2011-2021}A full list of my papers, most of which are in Russian, can be found via the links: \href{https://scholar.google.ru/citations?user=V_XLJ0kAAAAJ&hl=en}{Google Scholar}, \href{https://elibrary.ru/author_items.asp?authorid=640419&pubrole=100&show_refs=1&show_option=0}{eLIBRARY.RU}

\vspace{2em}
\hrule


\section*{Working Papers}
\noindent
\years{2022}Tereshchenko, Dmitrii, Competition among Russian Grocery Stores: Database on St. Petersburg, 2017-2021 (November 14, 2022). Higher School of Economics Research Paper No. WP BRP 258/EC/2022, Available at SSRN: \url{https://ssrn.com/abstract=4276261} or \url{http://dx.doi.org/10.2139/ssrn.4276261}.

\vspace{1em}

\years{2021}Gaivoronskaia, Elizaveta and Iskhakov, Fedor and Karmeliuk, Maria and Kokovin, Sergey and Ozhegov, Evgeniy and Ozhegova, Alina and Tereshchenko, Dmitrii, Competition Among Russian Grocery Stores: Facts and Hypotheses to Explore (November 6, 2021). Available at SSRN: \url{http://dx.doi.org/10.2139/ssrn.3957743}. 

\vspace{2em}
\hrule


\section*{Lifelong Education}
\noindent
I do my best to improve throughout my life and periodically participate in various courses and continuing education programmes, both online and in person.
\vspace{1em}

\years{2022}\textit{Writing academic articles: strengthening your chances for publication}, HSE University (32 hours).\\
\years{2022}\textit{Causal econometrics}, Egor Gaidar Foundation (72 hours).\\
\years{2020}\textit{Information and data presentation. Presentation creation}, HSE University (24 hours).\\
\years{2019}\textit{Basics of writing an empirical research paper}, HSE University (40 hours).\\
\years{2019}\textit{Empowering your academic writing in English: academic writing vs general writing}, HSE University (24 hours).\\
\years{2019}\textit{What an economist needs to know about data: selected socio-economic indicators}, European University at St. Petersburg and Yegor Gaidar Foundation.\\
\years{2017-2019}\textit{Applied econometric methods for research teachers}, HSE University and Egor Gaidar Foundation (342 hours).\\
\years{2018}\textit{Python programming for data collection and analysis}, HSE University (32 hours).\\
\years{2018}\textit{A to Z econometrics}, HSE University (72 hours).\\
\years{2018}\textit{Quantitative research data processing with MS Excel and IBM SPSS Statistic software}, Petrozavodsk State University (36 hours).\\
\years{2016-2018}{\textit{Modern microeconomics}, New Economic School and Yegor Gaidar Foundation (400 hours).\\
\years{2016}\textit{Cultural diversity and income inequality}, New Economic School’s Center for the Study of Diversity and Social Interactions (52 hours).\\
\years{2016}\textit{Sociocultural and economic development of regions: Eastern vector}, New Economic School’s Center for the Study of Diversity and Social Interactions (72 hours).\\
\years{2016}{\textit{Game theory}, Lomonosov Moscow State University and Yegor Gaidar Open University (70 hours).\\
\years{2016}{\textit{History of economic thought}, Lomonosov Moscow State University and Yegor Gaidar Open University (50 hours).\\
\years{2015}{\textit{Culture, institutions and diversity}, New Economic School’s Center for the Study of Diversity and Social Interactions (60 hours).\\
\years{2015}{\textit{Econometrics: introduction to time series and panel data analysis}, Lomonosov Moscow State University and Yegor Gaidar Open University (40 hours).\\
\years{2014-2015}{Education of professional and entrepreneurial skills through entrepreneurial spirit and advice for aspiring entrepreneurs}, Vienna University of Economics and Business (72 hours).\\
\years{2014}{\textit{Econometrics. Introductory course}, Yegor Gaidar Foundation.\\
\years{2013-2015}{\textit{Modern macroeconomics}, New Economic School and Yegor Gaidar Foundation (350 hours).\\
\years{2013}{\textit{Microeconomics. Teaching methods in economics}, Yegor Gaidar Foundation (72 hours).\\
\years{2013}{Formation of professional competencies of university teachers in distance learning}, Petrozavodsk State University (72 hours).\\
\years{2013}\textit{Organisation of students' independent work in the framework of competence model of graduates}, Petrozavodsk State University (24 hours).\\
\years{2012}\textit{Actual issues of pedagogy and psychology of higher education}, Petrozavodsk State University.


%\vspace{1cm}
\vfill{}
%\hrulefill

\begin{center}
	{\scriptsize  Date of compilation: \today}
\end{center}

\end{document}
